Porting the Steel Bank Common Lisp Compiler and Runtime to the Nintendo Switch NX Platform

### 2025-04-10 els2025-sbcl-nx/paper.tex
Fix another sentence.

\section{Relocation}\label{relocation}
Lisp objects contain absolute pointers, meaning when the in-process state of all Lisp memory spaces is dumped to disk, the resulting \textit{core image} is filled with absolute pointers. Traditionally, image-based Lisp implementations such as SBCL map their address spaces to fixed addresses for two reasons: First, reloading an image into a process is easier this way, since objects can be mapped back in the new image directly to where they were in the process that dumped the image. Second, some architecture backends optimize code generation by hardwiring the address of certain Lisp objects directly into the machine code.

>>>>

\section{Relocation}\label{relocation}
Lisp objects in memory contain absolute pointers, with the result that dumping the in-process state of all Lisp memory spaces to disk results in a \textit{core image} filled with absolute pointers. Traditionally, image-based Lisp implementations such as SBCL map their address spaces to fixed addresses for two reasons: First, reloading an image into a process is easier this way, since objects can be mapped back in the new image directly to where they were in the process that dumped the image. Second, some architecture backends optimize code generation by hardwiring the address of certain Lisp objects directly into the machine code.
